\documentclass[10pt,a4paper]{article}
\usepackage[margin=1.8cm]{geometry}
\usepackage{enumitem}
\usepackage{booktabs}
\usepackage{hyperref}
\usepackage{titlesec}

\titlespacing*{\section}{0pt}{6pt}{2pt}
\titlespacing*{\subsection}{0pt}{4pt}{2pt}
\setlength{\parskip}{2pt}
\setlength{\parindent}{0pt}

\title{\vspace{-1.5cm}\textbf{Supervision Meeting Report}\\[4pt]
\large Explainable Disease Progression \& Counterfactual Video Generation}
\author{Mohamed Boufafa \\ Supervisor: Dr.~Belkacem Chikhaoui \\ Mitacs Globalink -- T\'ELuQ University}
\date{March 11, 2026}

\begin{document}
\maketitle
\vspace{-0.5cm}

\section{Meeting Summary}

\textbf{Attendees:} Mohamed Boufafa, Dr.~Belkacem Chikhaoui \\
\textbf{Objective:} Review dataset acquisition progress and agree on Phase~1 work plan.

\section{Dataset Selection}

The \textbf{Cyprus PROTEAS Brain Metastases} dataset (Flouri et al., 2025) was confirmed for Objective~1. It provides 40 unique patients (45 directories), 186 longitudinal MRI timepoints across 4 sequences (T1, T2, T1c, FLAIR), expert tumor segmentations, CT scans, radiotherapy dose maps, and pre-extracted radiomic features. The dataset is already preprocessed to BraTS standard (1$\times$1$\times$1~mm\textsuperscript{3} isotropic, co-registered, skull-stripped).

\section{Phase 1 Plan Agreed}

\textbf{Phase 1 -- Oncology Medical Imaging Preparation and Exploration}\\
\textbf{Duration:} 2 weeks (Weeks 1--2)

\subsection*{Activities}
\begin{itemize}[nosep, leftmargin=1.5em]
    \item Selection and acquisition of public cancer imaging datasets (TCGA, BraTS, and/or LIDC-IDRI).
    \item Preprocessing of medical images (MRI/CT):
    \begin{itemize}[nosep, leftmargin=1em]
        \item Intensity normalization.
        \item Spatial resampling.
        \item Longitudinal image alignment across time points.
    \end{itemize}
    \item Verification and processing of tumor annotations when available.
    \item Exploratory data analysis:
    \begin{itemize}[nosep, leftmargin=1em]
        \item Distribution of tumor sizes and locations.
        \item Inter-patient and temporal variability analysis.
    \end{itemize}
    \item Organization of longitudinal patient imaging sequences.
\end{itemize}

\subsection*{Deliverables for Next Meeting}
Since the dataset is already preprocessed to BraTS standard, the preprocessing pipeline reduces to a validation step. The deliverables are:
\begin{enumerate}[nosep, leftmargin=1.5em]
    \item Cleaned, standardized, and temporally organized dataset with preprocessing validation report.
    \item Exploratory data analysis report with detailed methodology documentation.
    \item Longitudinal timeline CSV with exact visit day intervals.
    \item Progress summary for Phase~1 completion.
\end{enumerate}

\section{Next Steps}
Complete the Phase~1 EDA and preprocessing validation by the next meeting. Phase~2 will focus on feature extraction using temporal-aware architectures (Swin UNETR, TaViT) and integrating radiomic trajectories with clinical outcome data.

\end{document}
